RNAseq aCRY pCRY data dive

### 2024-04-21 2_A_dive_aCRY_pCRY/2_A_dive_aCRY_pCRY.Rmd
Rstudio fix
move folder

---
title: "RNAseq aCRY pCRY data dive"
author: "Kelterborn"
date: "2024-04-19"
output:
  github_document:
    html_preview: false
    toc: true
always_allow_html: true
editor_options: 
  chunk_output_type: console
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file,output_file= 'Readme.md')
    })
---

@@

# Macbook
scriptdir <- rstudioapi::getSourceEditorContext()$path
gitdir <- scriptdir %>% dirname() %>% dirname()
dir <- gitdir %>% dirname()

@@

### 3. Plot counts
####

>>>>

---
title: "RNAseq aCRY pCRY data dive"
author: "Kelterborn"
date: "2024-04-19"
output:
  github_document:
    html_preview: false
    toc: true
always_allow_html: true
editor_options: 
  chunk_output_type: console
knit: (function(input_file, encoding) {
    })
    rmarkdown::render(input_file,output_file= 'Readme.md')
---

@@

# Macbook
scriptdir <- rstudioapi::getSourceEditorContext()$path
gitdir <- scriptdir %>% dirname() %>% dirname()
dir <- "/Users/simonkelterborn/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/NGS (RNA-Seq & CRISPR)/Chlamy RNA-Seq aCRY"

@@

# 3. Results
## - Plot Counts
